DRAFT: v6 \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\

### 2025-09-22 main.tex
Updated the tex files to v6.

\title{
  DRAFT: v6.dev \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}

@@

\color{black}
\begin{abstract}
  % NOTE: keep to 150 words max
  We evaluated road-induced vibrations with dummies representing infants aged 0,
  3, and 9 months with five strollers and two cargo bicycles on six common road
  surfaces using the ISO standard for whole-body vibration. Strollers induced on
  average 0.4~\si{\mps\squared} on tarmac and up to 5.0~\si{\mps\squared} on
  cobblestones at a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
  induced as low as 0.6~\si{\mps\squared} on tarmac and up to
  10.7~\si{\mps\squared} at 25~\si{\kph} on paver bricks. The standard suggests
  that the highest accelerations for the strollers and cargo bicycles should be
  limited to continuous duration less than 10~\si{\minute}. Effects of body size
  and posture were minor. Two vintage stroller designs significantly reduced
  vibrations compared to three modern strollers, indicating the benefits of
  compliant suspensions. 
\end{abstract}

@@

\subsection{ISO Frequency Weighting and Bandwidth}
%
We report RMS accelerations as well as the ISO~2631-1 weighted accelerations for
comparison. Vibrations at frequencies between \SIrange{4}{11}{\hertz} showed to
have the largest unweighted magnitude, but there are substantial accelerations
at higher frequencies, as shown by the unweighted 80\% bandwidth. Our results
show substantial differences between RMS and VDV, highlighting the importance of
reviewing their meaning. These differences emerge from the high bandwidth of the
accelerations now measured, which greatly exceed the bandwidth of accelerations
measured with adults seated in cars (see e.g. Figure 2 in
\cite{griffin2004experimental}). Adult experiments show that significant
discomfort can be measured across all tested frequencies being 80 Hz
\cite{morioka2010frequency} or even 315~\si{\hertz}~\cite{morioka2006magnitude}
albeit with reduced sensitivity.

@@

    and posture to ensure that their designs isolate vibrations well for all use

@@

\subsection{Acknowledgement}
%
Niel Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Idsart
Kignma, Darek Wieckowksi, Aernout Dijkstra-Hellinga, and  Clement Moe all
provided important feedback on the preprint that helped improve the paper. This
work was financially supported by VeiligheidNL under the ``Project Trillingen
bakfiets en wandelwagen.''

@@

\subsection{Data Availability Statement}
%
TODO

@@

\section{Additional Exploratory Statistics}
\subsection{Effect of Speed}
%
Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1
weighted vertical RMS acceleration across the tested speeds. On paver
bricks, the RMS acceleration increased by approximately 1.6\(\times\) when increasing
the speed from \SIrange{12}{25}{\kilo\meter\per\hour}.The effect of speed while cycling on tarmac was less drastic, but still showed a slight increase.

\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
  \caption{Seat pan ISO 2631-1 weighted vertical acceleration RMS versus speed
  for all cargo bicycle repetitions. Shaded regions represent the 95\%
  confidence intervals from a simple linear regression that ignores
  \(x_\textrm{Cargo Bicycle}\).}
  \label{fig:compare-bicycle-speed}
\end{figure}
%
\subsection{Effect of Dummy Size}
%
Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
acceleration for each repetition for all vehicles, and compares the dummy sizes.
Substantial variation has been shown to relate significantly to the surface and
within cargo bicycles, as well as to speed (see tables
\ref{tab:sig-group-stroller},\ref{tab:sig-group-bicycle}).
%There were larger accelerations in the bicycle (high speeds) versus the stroller (low speeds), likely mostly attributed to the different testing speeds. 
When comparing the vertical RMS acceleration values between cargo bicycles and
strollers, there are no obvious differences due to baby size, i.e. each dummy
size experienced a similar range of acceleration magnitudes when the vehicle type
and the road surface are ignored. For bicycles, the lightest dummy sometimes
experienced a higher acceleration than the heavier dummy, but high and low
accelerations were observed across the tested speed range.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
  baby age (and thus size \& mass) for all repetitions with colour indicating
  the mean speed of the trial. The lightest colour dots are strollers (4 km/h) and the
  remaining are cargo bicycles (8-24 km/h).}
  \label{fig:compare-baby-mass}
\end{figure}

@@

\paragraph{Concerning the development of a benchmark:}
%
At this moment, no requirements exist for the vibrational properties of child
transport systems in the standards for strollers, cargo bicycles, bicycle seats, bicycle trailers,
and car seats. Due to the magnitude of vibrations that can occur during child
transport, it is imperative to include requirements for the vibrational
properties in the standards for these products. %At this moment, no new requirements can be defined because there is not enough information. With the information resulting from more research on infant vibration, a benchmark for the vibration properties of infant transportation products needs to be developed. 
Tests as performed in this study mark a first milestone. Road surfaces, speeds, dummies, posture, and metrics could be standardised. Over the years, these could be refined building upon scientific research. Acceptance thresholds could be set to accept current products that perform well.  This will enable the inclusion of (minimal) requirements for vibration
properties in the standards, which would greatly increase the health and comfort
of infants who must use these products.

@@

We considered the use of ``crash test dummies'' (also known as anthropomorphic
test devices or ATDs), which are designed and commonly used to test child seats
in car crash tests. However, the closest available body sizes for crash test
dummies do not meet the body sizes desired for this investigation. Furthermore,
crash test dummies are of a fundamentally different design, based on scaling of
adult biomechanical data rather than child data and with dynamic properties
designed for crash conditions, not for vibration testing. Therefore, crash test
dummies were not considered a good option to use for the envisaged vibration tests. 
 The following lists the dummies used:
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})

@@

\begin{description}
\item[Strollers] A selection of vintage and modern strollers for carrying
infants. The modern strollers are configurable as cots for newborns and as seats
for older infants.
%
\begin{description}
  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
  it an all-terrain stroller, according to the manufacturer. It has large
  puncture-resistant tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
  \item[Green Machine] An unknown brand vintage perambulator with a cot, dating
  approximately from the 1970s that includes a leather strap suspended cot in a
  metal frame. The wheels are relatively large compared to modern strollers.
  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-6
  months) and an infant seat option. It has large wheels with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-Cosi website})
  \item[Old Rusty] An unknown brand vintage seat-style stroller dating approximately from the 1970s that includes a metal spring suspension system and wheels that are slightly larger than those on modern strollers.
  \item[Stokke BABYZEN YOYO 0+] Among the smallest foldable strollers on the market. It has only a marginal suspension system and smaller wheels compared to other strollers available on the market.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
\end{description}
\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
seats can be mounted.
%
\begin{description}
  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
  rear) cargo tricycle without electric assist. This vehicle will not roll into
  curves. However, differing road surface unevenness at the left and right front
  wheels will induce lateral roll and lateral acceleration in infants. We added
  masses in specific locations to simulate the presence of an electric motor and
  battery package, in order to compare the results with those of the Urban Arrow. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
  Webpage}) 
  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in the Netherlands. This vehicle has two inline wheels, which makes it roll into curves like a regular bicycle. It is featured by a long frame that can carry loads (e.g., a child in a car seat or a baby shell) placed in between the rider and the front wheel. 
  (\href{https://urban arrow.com/}{Urban Arrow website})
\end{description}
\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
cargo bicycles.
%
\begin{description}
  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
  cargo bicycles.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
    Webpage})
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
  adapter was used in both cargo bicycles.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
    Webpage})
\end{description}
\end{description}

@@

\section{Location and pictures of the experiment areas}
\label{app:location}
%
\begin{itemize}
  \item \textbf{Strollers} were tested with dummies of 0 months and 9 months at
  5~\si{\kph} at:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks % Klinkers
      \item Sidewalk pavers % Stoeptegels
      \item Cobblestones 
      \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar 
  \end{itemize}
  \item \textbf{Cargo bicycles} were tested with dummies of 0 months and 3
  months. Test were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
  was also tested at 25~\si{\kph} whereas the Keiler was tested at
  20~\si{\km\per\hour} for safety reasons (due to wobbling). The test surfaces
  are:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks
      \item Shock bump: A 30~\si{\mm} x 30~\si{\mm} square section aluminium bar (also tested at 5~\si{\kph})
      \end{itemize}
  \item \textbf{Baby seats} Both the Pebble and the
  Melia was tested on each cargo bicycle using the same mounting
  systems.
\end{itemize}

>>>>

\title{
  DRAFT: v6 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}

@@

\color{black}
\begin{abstract}
  % NOTE: keep to 150 words max
  % Knowledge is lacking on road-induced vibrations for infants transported  in
  % strollers and cargo  bicycles.
  We evaluated vibrations with dummies representing infants aged 0, 3, and 9
  months lying or sitting in five strollers and two cargo bicycles with
  dedicated baby seats on six common road surfaces using the ISO standard for
  whole-body vibration.
  Strollers induced on average 0.4~\si{\mps\squared} on tarmac and up to
  5.0~\si{\mps\squared} on cobblestones at a mean walking speed of
  5.3~\si{\kph}.
  Cargo bicycles induced on average 0.6~\si{\mps\squared} on tarmac and up to
  10.7~\si{\mps\squared} at 25~\si{\kph} on paver bricks.
  The standard suggests the highest accelerations for strollers and cargo
  bicycles are extremely uncomfortable and continuous exposure should be limited
  to less than 10~\si{\minute}.
  % Effects of body size and posture were minor.
  Two vintage strollers significantly reduced vibrations compared to three
  modern strollers, indicating benefits of compliant suspensions. 
  We recommend designers systematically consider vibration, users avoid
  prolonged exposure to surfaces rougher than tarmac, and researchers to pursue
  scientifically founded test procedures and standards for infant vibration.
\end{abstract}

@@

\subsection{ISO Frequency Weighting and Bandwidth}
%
We report RMS accelerations as well as the ISO~2631-1 weighted accelerations for
comparison. Vibrations at frequencies between \SIrange{4}{11}{\hertz} showed to
have the largest unweighted magnitude, but there are substantial accelerations
at higher frequencies, as shown by the unweighted 80\% bandwidth. Our results
show substantial differences between RMS and VDV, highlighting the importance of
reviewing their meaning. These differences emerge from the high bandwidth of the
accelerations now measured, which greatly exceed the bandwidth of accelerations
measured with adults seated in cars (see e.g. Figure 2 in
\cite{griffin2004experimental}). Adult experiments investigating discomfort as a function of frequency, show that significant
discomfort can be measured across all tested frequencies, being up to 80 Hz
\cite{morioka2010frequency} or even up to 315~\si{\hertz}~\cite{morioka2006magnitude}
albeit with reduced sensitivity.

@@

    and postures to ensure that their designs isolate vibrations well for all use

@@

\subsection{Acknowledgement}
%
Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Idsart
Kingma, Darek Wieckowksi, Aernout Dijkstra-Hellinga, and  Clement Moe all
provided important feedback on the preprint that helped improve the paper. This
work was financially supported by VeiligheidNL under the ``Project Trillingen
bakfiets en wandelwagen.''

@@

\subsection{Data Availability Statement}
%
The data will be made publicly available alongside publication.

@@

\section{Additional Exploratory Statistics}
\subsection{Effect of Speed}
%
Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1
weighted vertical RMS acceleration across the tested speeds. On paver
bricks, the RMS acceleration increased by approximately 1.6\(\times\) when increasing
the speed from \SIrange{12}{25}{\kilo\meter\per\hour}.The effect of speed while cycling on tarmac was less drastic, but still showed a slight increase.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
  \caption{Seat pan ISO 2631-1 weighted vertical acceleration RMS versus speed
  for all cargo bicycle repetitions. Shaded regions represent the 95\%
  confidence intervals from a simple linear regression that ignores
  \(x_\textrm{Cargo Bicycle}\).}
  \label{fig:compare-bicycle-speed}
\end{figure}

\subsection{Effect of Dummy Size}
%
Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
acceleration for each repetition for all vehicles, and compares the dummy sizes.
Substantial variation has been shown to relate significantly to the surface and
within cargo bicycles, as well as to speed (see tables
\ref{tab:sig-group-stroller},\ref{tab:sig-group-bicycle}).
%There were larger accelerations in the bicycle (high speeds) versus the stroller (low speeds), likely mostly attributed to the different testing speeds. 
When comparing the vertical RMS acceleration values between cargo bicycles and
strollers, there are no obvious differences due to baby size, i.e. each dummy
size experienced a similar range of acceleration magnitudes when the vehicle type
and the road surface are ignored. For bicycles, the lightest dummy sometimes
experienced a higher acceleration than the heavier dummy, but high and low
accelerations were observed across the tested speed range.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
  baby age (and thus size \& mass) for all repetitions with colour indicating
  the mean speed of the trial. The lightest colour dots are strollers (4 km/h) and the
  remaining are cargo bicycles (8-24 km/h).}
  \label{fig:compare-baby-mass}
\end{figure}

@@

\paragraph{Concerning the development of a benchmark:}
%
At this moment, no requirements exist for the vibrational properties of child
transport systems in the standards for strollers, cargo bicycles, bicycle seats,
bicycle trailers, and car seats. Due to the magnitude of vibrations that can
occur during child transport, it is imperative to include requirements for the
vibrational properties in the standards for these products. At this moment, it
is difficult to develop new requirements because there is not enough
information. With the information resulting from more research on infant
vibration, a benchmark for the vibration properties of infant transportation
products needs to be developed. Tests as performed in this study mark a first
milestone. Road surfaces, speeds, dummies, posture, and metrics could be
standardised. Over the years, these could be refined building upon scientific
research. Acceptance thresholds could be set to accept current products that
perform well.  This will enable the inclusion of (minimal) requirements for
vibration properties in the standards, which would greatly increase the health
and comfort of infants who must use these products.

@@

We considered the use of ``crash test dummies'' (also known as anthropomorphic
test devices or ATDs), which are designed and commonly used to test child seats
in car crash tests. However, the closest available body sizes for crash test
dummies do not meet the body sizes desired for this investigation. Furthermore, crash test dummies are of a fundamentally different design, based on scaling of adult biomechanical data rather than child data and with dynamic properties designed for crash conditions, not for vibration testing. Therefore, crash test dummies were not used for the envisaged vibration tests. 
 The following lists the dummies used:
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})

@@

\begin{description}
\item[Strollers] A selection of vintage and modern strollers for carrying
infants. The modern strollers are configurable as cots for newborns and as seats
for older infants.
\begin{description}
  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
  it an all-terrain stroller, according to the manufacturer. It has large
  puncture-resistant tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
  \item[Green Machine] An unknown brand vintage perambulator with a cot, dating
  approximately from the 1970s that includes a leather strap suspended cot in a
  metal frame. The wheels are relatively large compared to modern strollers.
  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-6
  months) and an infant seat option. It has large wheels with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-Cosi website})
  \item[Old Rusty] An unknown brand vintage seat-style stroller dating approximately from the 1970s that includes a metal spring suspension system and wheels that are slightly larger than those on modern strollers.
  \item[Stokke BABYZEN YOYO 0+] Among the smallest foldable strollers on the market. It has only a marginal suspension system and smaller wheels compared to other strollers available on the market.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
\end{description}
\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
seats can be mounted.
\begin{description}
  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the rear)
  cargo tricycle without electric assist. This vehicle will not roll into
  curves. However, differing road surface unevenness at the left and right front
  wheels will induce lateral roll and lateral acceleration in infants. We added
  masses in specific locations to simulate the presence of an electric motor and
  battery package, in order to compare the results with those of the Urban
  Arrow. The tricycle was equipped with tyres CST XPEDIUM Safe 47-559
  (Cheng Shin Tire, Yuanlin, Taiwan) on the rear, and Schwalbe Green Comfort Road Cruiser
  K-Guard 3 47-507 (Ralf Bohle GmbH, Reichshof-Wehnrath, Germany) on
  the front. We set both tyres to an inflation pressure of 300~\si{\kPa}.
  (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in
  the Netherlands. This vehicle has two inline wheels, which makes it roll into
  curves like a regular bicycle. It is featured by a long frame that can carry
  loads (e.g., a child in a car seat or a baby shell) placed in between the
  rider and the front wheel. We used the ''Family Performance Plus'' model, with
  an electric drivetrain from Bosch Performance Line (65~\si{\N}\si{\m},
  250~\si{\W}). It was equipped with tyres Schwalbe Big Ben Plus 55-559 on the
  rear, and Schwalbe Big Ben Plus 55-406 on the front (Ralf Bohle GmbH, Reichshof-Wehnrath, Germany). We set both tyres to an
  inflation pressure of 300~\si{\kPa}, according to the range recommended by the
  manufacturer.
  (\href{https://urban arrow.com/}{Urban Arrow website})
\end{description}
\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
cargo bicycles.
\begin{description}
  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
  cargo bicycles.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
    Webpage})
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
  adapter was used in both cargo bicycles.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
    Webpage})
\end{description}
\end{description}

@@

\section{Location and pictures of the experiment areas}
\label{app:location}
%
\begin{itemize}
  \item \textbf{Strollers} were tested with dummies of 0 months and 9 months at
  5~\si{\kph} at:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks % Klinkers
      \item Sidewalk pavers % Stoeptegels
      \item Cobblestones 
      \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar 
  \end{itemize}
  \item \textbf{Cargo bicycles} were tested with dummies of 0 months and 3
  months. Tests were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
  was also tested at 25~\si{\kph} whereas the Keiler was tested at
  20~\si{\km\per\hour} for safety reasons (due to wobbling). The test surfaces
  are:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks
      \item Shock bump: A 30~\si{\mm} x 30~\si{\mm} square section aluminium bar (also tested at 5~\si{\kph})
      \end{itemize}
  \item \textbf{Baby seats} Both the Pebble and the
  Melia was tested on each cargo bicycle using the same mounting
  systems.
\end{itemize}
